Title page

### 2024-09-04 output/Title_page.Rmd
Versions title page with title and author data

---
title: "Title page"
---

- Article title
- The full list of authors including names and affiliations of each
    - The listed affiliation should be the institution where the research was
    conducted. If an author has moved to a new institution since completing the
    research, the new affiliation can be included in a note at the end of the
    manuscript – please indicate this on the title page.
    - All persons eligible for authorship must be included at the time of
    submission (please see the authorship section for more information).
    - Contact information for the corresponding author: name, institutional
    address, phone, email
- Statements and Declarations section

>>>>

---
title: "Title page"
output:
  officedown::rdocx_document:
    mapstyles:
      Body Text: ['First Paragraph', 'Abstract']
    base_format: bookdown::word_document2
    reference_docx: ../../www/Template.docx
    number_sections: no
    keep_md:         no
    fig_width:       4
    fig_height:      4
editor_options: 
  chunk_output_type: console
---

**Article title:**
A generalized definition of multidimensional item response theory parameters

**Short title:** Generalized MIRT parameters

**List of authors:**

- Daniel Morillo-Cuadrado. Department of Behavioral Science Methodology,
  Faculty of Psychology, National Remote Education University (UNED), Spain.

- Mario Luzardo-Verde. Department of Mathematics and Applications, La República
  University, Uruguay.

**Corresponding author:**

Daniel Morillo-Cuadrado \\
Faculty of Psychology, Office 2.74.
C. de Juan del Rosal 10, 28040 Madrid

Phone nº: +34 91398 6584
Email address: dvmorillo@psi.uned.es
